Which ITG Stepcharts are Turniest?

### 2017-03-15 itg/2/paper.tex
make heuristic alg more concise
change some stuff up

It is tempting to assign the facings $L$, $U$, $U$, and $R$ respectively to the $LL$, $DD$, $UU$, and $RR$ footswitches.
However, Figure~\ref{fig:fs}(c) shows that if a footswitch begins with a crossover on $U$, the facing should be reversed:
the $RR$ footing should face $L$, and $LL$ should face $R$.
``Backwards footswitches'' with $D$ facing are also theoretically possible,
arising from patterns such as $LURDDL$ or $LDRUUL$, although I know of no real-world chart which does this (hmm, tempting...).

@@

\begin{figure}[t]
	\begin{center}
	\begin{tabular}{c}
		\includegraphics[width=0.16\textwidth]{paradise-lost-false-positive.png}
		\\
		(a) Paradise Lost \\
		(16, Cirque du Lykan)
	\end{tabular}
	%\begin{tabular}{c}
	%	\includegraphics[width=0.16\textwidth]{false-positive-toromi-hearts.png}
	%	\\
	%	(a) Toromi Hearts 2 \\
	%	(18, Cirque du Zonda)
	%\end{tabular}
	\begin{tabular}{c}
		\includegraphics[width=0.16\textwidth]{hearbeat-rollstream-doublestep.png}
		\\
		(b) Heartbeat \\
		(13, TranceNation)
	\end{tabular}
	\end{center}
	\caption{The doublesteps in some streamy charts must be identified, and the stream split, lest ``too much'' of the following stream appear completely crossed-over.}
	\label{fig:force-doublestep}
\end{figure}

\newcommand\Stream{\ensuremath{\mathcal{S}}}
\newcommand\Doublestep{\ensuremath{\mathcal{DS}}}
\newcommand\nflip{\ensuremath{n_{\mathfrak{flip}}}}
\newcommand\percentmatch{\ensuremath{\%_{\mathfrak{match}}}}
\begin{algorithm}[h!]
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Invariant}
	\Input{\Stream, a step sequence}
	\Output{$\forall s_i, s_j \in \Stream, j=i+1 \rightarrow \mathsf{\neg StreamBoundary}(s_i,s_j)$}
	\Input{\nflip, heuristic minimum length} %of flipped stream to doublestep into}
	\Input{$\percentmatch$, heuristic percentage, initially 0}
	\For{$i \in \mathsf{length}(\Stream) \wedge \neg {\sf defined}(i_{\Doublestep})$}{
		%$\mathcal{S}' \leftarrow \{ s_j | s_j \in \Stream \wedge j \ge i \}$ \\ %i \le j < i + \nflip \})$ \\
		$\Stream' \leftarrow \{ s_k | s_k \in \mathsf{LRs}(\{ s_j | s_j \in \Stream \wedge j \ge i \}) \wedge k \le \nflip \}$ \\
		%$\mathcal{X} \leftarrow \mathsf{CrossoverSteps}(\{ s_j | s_j \in \Stream \wedge i \le j < i + \nflip \})$ \\
		%$\mathcal{M} \leftarrow \mathsf{MatchingSteps} (\{ s_j | s_j \in \Stream \wedge i \le j < i + \nflip \})$
		\If{$|\Stream'| = \nflip \wedge |\mathsf{Matching}(\Stream')| \le \percentmatch \times (|\mathsf{Crossovers}(\Stream')| + |\mathsf{Matching}(\Stream')|)$}{
			$i_{\Doublestep} \leftarrow i$
		}
	}
	\eIf{{\sf defined}($i_{\Doublestep})$}{
		\If{$i_{\Doublestep} = 0$}{
			% gotta write "tail stream" as complicatedly as possible
			$i_{\Doublestep} \leftarrow \mathsf{FindUnflippedSection}(\{ s_i | s_i \in \Stream \wedge i \ne 0 \})$
			%\mathsf{tail}(\Stream))$
		}
		{\sf HeuristicallyDoublestep}($\{ s_i | s_i \in \Stream \wedge i < i_{\Doublestep} \}$)
		{\sf HeuristicallyDoublestep}($\{ s_i | s_i \in \Stream \wedge i \ge i_{\Doublestep} \}$)
	}{
		{\sf CommitStream}(\Stream)
	}
	\caption{{\sf HeuristicallyDoublestep}(\Stream)}
	\label{alg:heuristic}
\end{algorithm}

To handle such cases,
I extended the algorithm with a heuristic to identify when a stream becomes ``too crossed-over'' for ``too long'',
and to force a doublestep by splitting the stream to flip it back.
Algorithm~\ref{alg:heuristic} shows the implementation.
I will not summarize how it works due to space limitations, but the description should be intuitive enough.
The heuristic evaluated Figure~\ref{fig:force-doublestep}'s charts as having 0 crossovers and 1 and 21 doublesteps, respectively.
In my analysis next section, I will use $\nflip = 9$
(determined by inspection of a few favourite charts, which should be scientifically rigorous enough for anyone).

@@

@@

	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\

@@

		\multicolumn{5}{c}{\em no 8s- with $\ge$100 XOs} \\
		 9 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 107 & \em 8.7 \\
		10 & J-PARA SUPER MEGAMIX     & CuoReNeRo MeGaPacK    & \bf 141 & \em 3.9 \\
		11 & Somebody That I Used To Know & Best of Gazebo    & \bf 114 & \em 11.9 \\
		12 & Credens Justitiam        & Stuff B Likes         & \bf 136 & \em 12.4 \\
		13 & Banshee Strikes          & VocaJawnz             & \bf 152 & \em 10.2 \\
		14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		15 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 101 & \em 4.2 \\
		\multicolumn{5}{c}{\em no 16s-20s with $\ge$100 XOs} \\
		21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\

@@

		 4 & DAM DIRIRAM              & DDR 3rdMIX            & \em  30 & \bf 27.3 \\
		 5 & STRICTLY BUSINESS        & DDR 1st               & \em  33 & \bf 21.4 \\
		 6 & STRICTLY BUSINESS        & DDR 1st               & \em  38 & \bf 20.9 \\
		 7 & MOBO$\star$MOGA          & DDR EXTREME           & \em  37 & \bf 17.3 \\
		 8 & PARANOiA                 & DDR 1st               & \em  58 & \bf 19.6 \\
		 9 & Dazzlin Darlin           & r21twins              & \em  76 & \bf 22.0 \\
		10 & Enchanted Journey        & ITG Rebirth           & \em  78 & \bf 19.3 \\
		11 & Lune Noir                & r21freak Friendship   & \em  58 & \bf 13.4 \\
		12 & Winnipeg is Fucking Over & best of r21freak ii   & \em 122 & \bf 14.3 \\
		13 & The Sampling Paradise    & The Paradise Sampler  & \em 139 & \bf 15.6 \\
		14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		\multicolumn{5}{c}{\em no 15s-20s with $\ge$10\% XOs} \\
		21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

	\caption{Charts with the highest percentage of crossovers among total steps.}

@@

	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\

@@

		\multicolumn{5}{c}{\em no 5s- with $\ge$50 FSs} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		\multicolumn{5}{c}{\em no 7s-9s with $\ge$50 FSs} \\
		10 & Eat 'Em Up!      & Mute Sims 5           & \bf  54 & \em  9.0 \\
		11 & Nemeton          & The Legend of Zim 4   & \bf  97 & \em 10.3 \\
		12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		15 & Danse Macabre    & Aoreo's Ariginals     & \bf 201 & \em 12.2 \\
		16 & Weird Science    & Stamina Showcase      & \bf  61 & \em  1.8 \\
		\multicolumn{5}{c}{\em no 17s+ with $\ge$50 FSs} \\

@@

	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\

@@

		%\multicolumn{5}{c}{\em no <6s with >50 FSs} \\
		 3 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  26 & \bf 15.3 \\
		 4 & MAKE IT BETTER   & DDR 2ndMIX            & \em  26 & \bf 20.0 \\
		\multicolumn{5}{c}{\em no 5s with $\ge$10\% FS} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		 7 & 5.1.1            & DDR MAX               & \em  13 & \bf 12.9 \\
		\multicolumn{5}{c}{\em no 8s with $\ge$10\% FS} \\
		 9 & PARANOiA KCET    & DDR 2ndMIX            & \em  33 & \bf 10.2 \\
		10 & Delhi Ill        & Mute Sims 6           & \em  40 & \bf 11.6 \\
		11 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  75 & \bf 11.8 \\
		12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		15 & Flames of the Sky & fort rapids vii      & \em 172 & \bf 16.5 \\
		\multicolumn{5}{c}{\em no 16s+ with $\ge$10\% FS} \\

@@

	\caption{Charts with the highest percentage of footswitches among total steps.}

@@

	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XF & \bf XF\% \\

@@

		\multicolumn{5}{c}{\em no 8s- with $\ge$12 XFs} \\
		 9 & Dr. Boom-Bombay   & fort rapids vii            & \bf 18 & 4.0 \\
		10 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.5 \\
		11 & Heart Shooter     & VocaJawnz                  & \bf 44 & 5.1 \\
		12 & Beautiful Synergy & Keyboard Collaboration III & \bf 14 & 3.2 \\
		13 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.2 \\
		14 & Fancy Footwork    & Cirque du Zeppelin         & \bf 40 & 4.2 \\
		\multicolumn{5}{c}{\em no 14s+ with $\ge$12 XFs} \\

@@

@@

Please accept our paper.
I worked hard on it.

>>>>

It is tempting to assign the facings $L$, $U$, $U$, and $R$ respectively to the $LL$, $DD$, $UU$, and $RR$ footswitches.
However, Figure~\ref{fig:fs}(c) shows that if a footswitch begins with a crossover on $U$, the facing should be reversed:
the $RR$ footing should face $L$, and $LL$ should face $R$.
``Spin-switches'' with $D$ facing are also theoretically possible,
arising from patterns such as $LURDDL$ or $LDRUUL$, although I know of no real-world chart which does this (hmm, tempting...).

@@

\begin{figure}[t]
	\begin{center}
	\begin{tabular}{c}
		\includegraphics[width=0.18\textwidth]{paradise-lost-false-positive.png}
		\\
		(a) Paradise Lost \\
		(16, Cirque du Lykan)
	\end{tabular}
	%\begin{tabular}{c}
	%	\includegraphics[width=0.18\textwidth]{false-positive-toromi-hearts.png}
	%	\\
	%	(a) Toromi Hearts 2 \\
	%	(18, Cirque du Zonda)
	%\end{tabular}
	\begin{tabular}{c}
		\includegraphics[width=0.18\textwidth]{hearbeat-rollstream-doublestep.png}
		\\
		(b) Heartbeat \\
		(13, TranceNation)
	\end{tabular}
	\end{center}
	\caption{The doublesteps in some streamy charts must be identified, and the stream split, lest ``too much'' of the following stream appear completely crossed-over.}
	\label{fig:force-doublestep}
\end{figure}

\newcommand\Stream{\ensuremath{\mathcal{S}}}
\newcommand\Doublestep{\ensuremath{\mathcal{DS}}}
\newcommand\nflip{\ensuremath{n_{\mathfrak{flip}}}}
\newcommand\percentflip{\ensuremath{\%_{\mathfrak{flip}}}}
\begin{algorithm}[h!]
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Invariant}
	\Input{\Stream, a step sequence $s_0 \dots s_n$}
	\Output{$\forall s_i, s_j \in \Stream, j=i+1 \rightarrow \mathsf{\neg StreamBoundary}(s_i,s_j)$}
	\Input{\nflip, heuristic minimum length} %of flipped stream to doublestep into}
	\Input{$\percentflip$, heuristic percentage, initially 100}
	\For{$i \in \mathsf{length}(\Stream) \wedge \neg {\sf defined}(i_{\Doublestep})$}{
		$\Stream' \leftarrow \{ s_k | s_k \in \mathsf{LRs}(\{ s_j | s_j \in \Stream \wedge j \ge i \}) \wedge k \le \nflip \}$ \\
		\If{$|\Stream'| = \nflip$ $\wedge$ $|\mathsf{Crossovers}(\Stream')| \ge \percentflip \times |\Stream'|$}{
			$i_{\Doublestep} \leftarrow i$
		}
	}
	\eIf{{\sf defined}($i_{\Doublestep})$}{
		\If{$i_{\Doublestep} = 0$}{
			% gotta write "tail stream" as complicatedly as possible
			$i_{\Doublestep} \leftarrow \mathsf{FindUnflippedSection}(\{ s_i | s_i \in \Stream \wedge i \ne 0 \})$
			%\mathsf{tail}(\Stream))$
		}
		{\sf HeuristicallyDoublestep}($\{ s_i | s_i \in \Stream \wedge i < i_{\Doublestep} \}$)
		{\sf HeuristicallyDoublestep}($\{ s_i | s_i \in \Stream \wedge i \ge i_{\Doublestep} \}$)
	}{
		{\sf CommitStream}(\Stream)
	}
	\caption{{\sf HeuristicallyDoublestep}(\Stream)}
	\label{alg:heuristic}
\end{algorithm}

To handle such cases,
I extended the algorithm with a heuristic to identify when a stream becomes ``too crossed-over'' for ``too long'',
and to force a doublestep by splitting the stream to flip it back.
Algorithm~\ref{alg:heuristic} shows the implementation.
I will not summarize how it works due to space limitations, but the description should be intuitive enough.
The heuristic evaluated Figure~\ref{fig:force-doublestep}'s charts as having 0 crossovers each and 1 and 21 doublesteps, respectively.
In my analysis next section, I will use $\nflip = 9$
(determined by inspection of a few favourite charts, which should be scientifically rigorous enough for anyone).

@@

% Stuff to talk about.
% Dataset size now >10k
% I reran turniness on fancy footwork and it actually got turnier (double check dis), b/c of all the candles

% By author/by pack: I excluded 1s-3s, admittedly biased against konami, on the pretense of excluding nonsense false positives, but even after that, konami is still the crossover king
% Step authors are limited to 10 or more charts

% Miscellaneous charts I want to exhibit:
% Conflict forced doublesteps
% Heart shooter 'sidefoots'
% Boom Bombay - triple xover jack footed as sideswitch
% Toxic - jack+doublestep footed as sideswitch + xover stream instead
% H'ble mention to sandstorm for jacks

@@

	\begin{tabular}{r|l|l|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XO \\

@@

		\multicolumn{4}{c}{\em no 8s- with $\ge$100 XOs} \\
		 9 & MAX Forever              & CuoReNeRo & 107 \\
		10 & J-PARA SUPER MEGAMIX     & CuoReNeRo & 141 \\
		11 & Somebody I Used To Know    & Best of Gazebo    & 114 \\
		12 & Credens Justitiam        & Stuff B Likes         & 136 \\
		13 & Banshee Strikes          & VocaJawnz             & 152 \\
		14 & Slow Down                & Sexuality Violation 2 & 160 \\
		15 & MAX Forever              & CuoReNeRo & 101 \\
		\multicolumn{4}{c}{\em no 16s-20s with $\ge$100 XOs} \\
		21 & Teenage Dream            & Sexuality Violation 2 & 280 \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		%\hline
		%\multicolumn{5}{c}{\em no 8s- with $\ge$100 XOs} \\
		% 9 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 107 & \em 8.7 \\
		%10 & J-PARA SUPER MEGAMIX     & CuoReNeRo MeGaPacK    & \bf 141 & \em 3.9 \\
		%11 & Somebody That I Used To Know & Best of Gazebo    & \bf 114 & \em 11.9 \\
		%12 & Credens Justitiam        & Stuff B Likes         & \bf 136 & \em 12.4 \\
		%13 & Banshee Strikes          & VocaJawnz             & \bf 152 & \em 10.2 \\
		%14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		%15 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 101 & \em 4.2 \\
		%\multicolumn{5}{c}{\em no 16s-20s with $\ge$100 XOs} \\
		%21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

	\begin{tabular}{r|l|l|c}
		\bf Ft. & \bf Name & \bf Pack & \bf XO\% \\

@@

		 4 & DAM DIRIRAM              & DDR 3rdMIX            & 27.3 \\
		 5 & STRICTLY BUSINESS        & DDR 1st               & 21.4 \\
		 6 & STRICTLY BUSINESS        & DDR 1st               & 20.9 \\
		 7 & MOBO$\star$MOGA          & DDR EXTREME           & 17.3 \\
		 8 & PARANOiA                 & DDR 1st               & 19.6 \\
		 9 & Dazzlin Darlin           & r21twins              & 22.0 \\
		10 & Enchanted Journey        & ITG Rebirth           & 19.3 \\
		11 & Lune Noir                & r21freak Friendship   & 13.4 \\
		12 & W'peg is Fucking Over    & best of r21freak ii   & 14.3 \\
		13 & The Sampling Paradise    & The Paradise Sampler  & 15.6 \\
		14 & Slow Down                & Sexuality Violation 2 & 13.3 \\
		\multicolumn{4}{c}{\em no 15s-20s with $\ge$10\% XOs} \\
		21 & Teenage Dream            & Sexuality Violation 2 & 11.8 \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		%\hline
		% 4 & DAM DIRIRAM              & DDR 3rdMIX            & \em  30 & \bf 27.3 \\
		% 5 & STRICTLY BUSINESS        & DDR 1st               & \em  33 & \bf 21.4 \\
		% 6 & STRICTLY BUSINESS        & DDR 1st               & \em  38 & \bf 20.9 \\
		% 7 & MOBO$\star$MOGA          & DDR EXTREME           & \em  37 & \bf 17.3 \\
		% 8 & PARANOiA                 & DDR 1st               & \em  58 & \bf 19.6 \\
		% 9 & Dazzlin Darlin           & r21twins              & \em  76 & \bf 22.0 \\
		%10 & Enchanted Journey        & ITG Rebirth           & \em  78 & \bf 19.3 \\
		%11 & Lune Noir                & r21freak Friendship   & \em  58 & \bf 13.4 \\
		%12 & Winnipeg is Fucking Over & best of r21freak ii   & \em 122 & \bf 14.3 \\
		%13 & The Sampling Paradise    & The Paradise Sampler  & \em 139 & \bf 15.6 \\
		%14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		%\multicolumn{5}{c}{\em no 15s-20s with $\ge$10\% XOs} \\
		%21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\

@@

	\caption{Charts with the highest percentage of XOs among total steps.}

@@

	\begin{tabular}{r|l|l|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#FS \\

@@

		\multicolumn{4}{c}{\em no 5s- with $\ge$50 FSs} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    &  56 \\
		\multicolumn{4}{c}{\em no 7s-9s with $\ge$50 FSs} \\
		10 & Eat 'Em Up!      & Mute Sims 5           &  54 \\
		11 & Nemeton          & The Legend of Zim 4   &  97 \\
		12 & Nemeton          & Subluminal            & 140 \\
		13 & Love Is Eternity & Subluminal            & 140 \\
		14 & Switch           & Getty                 & 347 \\
		15 & Danse Macabre    & Aoreo's Ariginals     & 201 \\
		16 & Weird Science    & Stamina Showcase      &  61 \\
		\multicolumn{4}{c}{\em no 17s+ with $\ge$50 FSs} \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		%\hline
		%\multicolumn{5}{c}{\em no 5s- with $\ge$50 FSs} \\
		% 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		%\multicolumn{5}{c}{\em no 7s-9s with $\ge$50 FSs} \\
		%10 & Eat 'Em Up!      & Mute Sims 5           & \bf  54 & \em  9.0 \\
		%11 & Nemeton          & The Legend of Zim 4   & \bf  97 & \em 10.3 \\
		%12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		%13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		%14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		%15 & Danse Macabre    & Aoreo's Ariginals     & \bf 201 & \em 12.2 \\
		%16 & Weird Science    & Stamina Showcase      & \bf  61 & \em  1.8 \\
		%\multicolumn{5}{c}{\em no 17s+ with $\ge$50 FSs} \\

@@

	\begin{tabular}{r|l|l|c}
		\bf Ft. & \bf Name & \bf Pack & \bf FS\% \\

@@

		 3 & Sweat Shop       & ITG Rebirth 2 Beta    & 15.3 \\
		 4 & MAKE IT BETTER   & DDR 2ndMIX            & 20.0 \\
		\multicolumn{4}{c}{\em no 5s with $\ge$10\% FS} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    & 18.2 \\
		 7 & 5.1.1            & DDR MAX               & 12.9 \\
		\multicolumn{4}{c}{\em no 8s with $\ge$10\% FS} \\
		 9 & PARANOiA KCET    & DDR 2ndMIX            & 10.2 \\
		10 & Delhi Ill        & Mute Sims 6           & 11.6 \\
		11 & Sweat Shop       & ITG Rebirth 2 Beta    & 11.8 \\
		12 & Nemeton          & Subluminal            & 14.8 \\
		13 & Love Is Eternity & Subluminal            & 16.8 \\
		14 & Switch           & Getty                 & 15.7 \\
		15 & Flames of the Sky & fort rapids vii      & 16.5 \\
		\multicolumn{4}{c}{\em no 16s+ with $\ge$10\% FS} \\
		%\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		%\hline
		% 3 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  26 & \bf 15.3 \\
		% 4 & MAKE IT BETTER   & DDR 2ndMIX            & \em  26 & \bf 20.0 \\
		%\multicolumn{5}{c}{\em no 5s with $\ge$10\% FS} \\
		% 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		% 7 & 5.1.1            & DDR MAX               & \em  13 & \bf 12.9 \\
		%\multicolumn{5}{c}{\em no 8s with $\ge$10\% FS} \\
		% 9 & PARANOiA KCET    & DDR 2ndMIX            & \em  33 & \bf 10.2 \\
		%10 & Delhi Ill        & Mute Sims 6           & \em  40 & \bf 11.6 \\
		%11 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  75 & \bf 11.8 \\
		%12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		%13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		%14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		%15 & Flames of the Sky & fort rapids vii      & \em 172 & \bf 16.5 \\
		%\multicolumn{5}{c}{\em no 16s+ with $\ge$10\% FS} \\

@@

	\caption{Charts with the highest percentage of FSs among total steps.}

@@

	\begin{tabular}{r|l|l|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XF \\

@@

		\multicolumn{4}{c}{\em no 8s- with $\ge$12 XFs} \\
		 9 & Dr. Boom-Bombay   & fort rapids vii            & 18 \\
		10 & Toxic             & Sexuality Violation 2      & 12 \\
		11 & Heart Shooter     & VocaJawnz                  & 44 \\
		12 & Beautiful Synergy & Keyboard Collaboration III & 14 \\
		13 & Toxic             & Sexuality Violation 2      & 12 \\
		14 & Fancy Footwork    & Cirque du Zeppelin         & 40 \\
		% 9 & Dr. Boom-Bombay   & fort rapids vii            & \bf 18 & 4.0 \\
		%10 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.5 \\
		%11 & Heart Shooter     & VocaJawnz                  & \bf 44 & 5.1 \\
		%12 & Beautiful Synergy & Keyboard Collaboration III & \bf 14 & 3.2 \\
		%13 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.2 \\
		%14 & Fancy Footwork    & Cirque du Zeppelin         & \bf 40 & 4.2 \\
		\multicolumn{4}{c}{\em no 15s+ with $\ge$12 XFs} \\

@@

\section{Never Work}

Let's be honest: this isn't gonna be a trilogy.

With that out of the way, here are some things that would be cool to implement in a fantasy universe with infinite free time.

% TODO
% forced doublesteps via holds
% - bracketjump footswitches - matador from valex 8
% understanding mine cues for doublesteps

@@

Please accept my paper.
I worked hard on it.
